\section{Introduction}

The Curry-Howard isomorphism shows the deep relationship between intuitionistic
logic and computation. Specifically, it establishes that proofs can be
interpreted as programs and proof reduction as computation. Because of this, we
can see that the different formalizations of intuitionistic logic will result in
different computational interpretations~\cite{DeYoung2020}.
Howard~\cite{Howard1980FormulaeAsTypes}, for example, established the connection
between natural deduction and the simply-typed $\lambda$-calculus.
Curry~\cite{doi:10.1073/pnas.20.11.584} took a different approach, associating
Hilbert-style proofs to combinators. Herbelin~\cite{Herbelin1995LambdaCalculusStructure}
established the system LJT based on the sequent calculus with a stoup, leading
to a computational interpretation featuring explicit substitutions.

Adding to this lineage, DeYoung et al.~\cite{DeYoung2020} presents the
semi-axiomatic sequent calculus (SAX), a formalization of intuitionistic logic
which arises by replacing all non-invertible rules in the sequent calculus with
axioms and leaving the invertible rules unchanged. The resulting system is
equivalent to $G_3$, but standard cut elimination fails: it is replaced by a
modified form in which certain analytic cuts, called snips, are permitted to
remain in normal-form proofs while preserving the subformula property.

Establishing these results is more involved than in the sequent calculus. Both
the admissibility of cut and the subformula property require tracking which
formula occurrences are eligible for a snip and which antecedents are
irrelevant, and both proofs require generalized induction hypotheses to account
for how the eligibility of formula occurrences changes through derivations. The
original paper necessarily leaves out many portions of the proofs implicit,
making SAX an interesting and non-trivial target for mechanization.

As such, we report on a mechanization \footnote{Available at
  \url{https://github.com/l4haie/mech-sax}.} of the proof theory of Soprillo, a
fragment of SAX in Beluga, a proof assistant with its foundations in contextual
modal logic and the Logical Framework. Beluga's explicit handling of contexts is
particularly suited to mechanizing SAX, precisely because we need to reason
about variables in contexts during our proof. Further, since it is an extension
of LF, we can build on the existing literature regarding mechanizing similar
systems and proofs in the
literature~\cite{crary2009substructural}~\cite{Pfenning2000StructuralCutElimination}.
This, to the best of our knowledge, is the first mechanization of SAX and its
proof theory. Specifically, we present:
\begin{itemize}
  \item A mechanization of the translation between SAX and $G_3$
  \item Mechanized proofs of cut admissibility, cut elimination, and the
    subformula property for Soprillo
\end{itemize}

The remainder of the paper is organized as follows: Section~\ref{section:motivation}
motivates the mechanization through SAX's computational interpretation and
illustrates the proof-theoretic subtleties that make it a challenging target.
Section~\ref{section:contribution} presents our mechanization in detail.
Section~\ref{section:related} discusses related work and
Section~\ref{section:conclusion} concludes.