\section{Contributions}
\label{section:contribution}

\subsection{Core Proof-Theoretic Results}

We mechanize the following proof-theoretic results for a representative
subset of SAX, covering identity, implication (${\supset}R$,
${\supset}L^0$), tensor (${\otimes}R^0$, ${\otimes}L$), and snips
($\texttt{snip}^1$, $\texttt{snip}^2$). The remaining connectives of
SAX (${\vee}$, ${\with}$, $\mathbf{1}$) follow the same patterns and are
left as future work.

\begin{theorem}[Translations between $G_3$ and SAX]
  $\Gamma \vdash A$ in $G_3$ iff $\Gamma \vdash A$ in SAX.
\end{theorem}

In the following theorems, a derivation is \emph{cut-free} if it
contains no uses of cut but may contain snips.

\begin{theorem}[Admissibility of Cut]
  If there are cut-free derivations of $\Gamma \vdash x : A$ and
  $\Gamma, x : A \vdash z : C$, there exists a cut-free derivation of
  $\Gamma \vdash z : C$.
\end{theorem}

\begin{theorem}[Cut Elimination in SAX]
  If there is a derivation of $\Gamma \vdash x : A$, there is a
  cut-free derivation of the same sequent.
\end{theorem}

\begin{theorem}[Subformula Property]
  All formulas in a cut-free derivation of $\Gamma \vdash x : A$ are
  subformulas of formulas in $\Gamma$ or $A$.
\end{theorem}

\subsection{Encoding SAX in Beluga}

We encode SAX in Beluga using HOAS. Hypotheses are represented as
variables in a context of schema \texttt{lctxS} with entries of type
\texttt{lhypS~A}. Derivations of $\Gamma \vdash A$ are terms of type
\texttt{[$\Gamma \vdash$  lconcS~A[]]}. Binding in rules such as ${\supset}R$
is handled by LF function types, so weakening and substitution are
inherited from the framework. The constructors of \texttt{lconcS}
correspond one-for-one to the rules of SAX; adequacy holds because
\texttt{lhypS} has no constructors, so its only inhabitants are context
variables.

\begin{lstlisting}
LF lhypS : o -> type = ;
LF lconcS : o -> type =
  | linitialS : {h : lhypS A} lconcS A
  | l⊃RS      : (lhypS A -> lconcS B) -> lconcS (A ⊃ B)
  | l⊃L0S     : lhypS A -> lhypS (A ⊃ B) -> lconcS B
  | lsnip1S   : {D : lconcS A} elig_c D -> (lhypS A -> lconcS B) -> lconcS B
  | lsnip2S   : lconcS A -> {E : lhypS A -> lconcS B} elig_h E -> lconcS B
  | l⊗R0S     : lhypS A -> lhypS B -> lconcS (A ⊗ B)
  | l⊗LS      : (lhypS A -> lhypS B -> lconcS C) -> lhypS (A ⊗ B) -> lconcS C
\end{lstlisting}

One notable feature of the encoding concerns the two variable annotations
from the paper's labeled calculus. Variables marked as \emph{irrelevant}
(superscript $0$) are those that appear as side formulas of an axiom or
identity and are never used in the derivation. In Beluga this annotation
is unnecessary: because LF has structural weakening, unused hypotheses
can simply be ignored. A derivation term in context $[\Gamma, x :
\texttt{lhypS}~A]$ where $x$ does not appear free can always be weakened
back to $[\Gamma]$, directly corresponding to dropping an irrelevant
antecedent. The irrelevance superscripts in the paper are therefore
absorbed into the framework's own treatment of unused variables.

\subsection{Eligibility as a Predicate on Derivation Terms}

The central design challenge is representing \emph{eligibility}. In the
paper, a variable occurrence in a derivation is eligible if it was
introduced by an axiom in an eligible position. The two forms of snip
differ in which premise must be eligible: $\texttt{Snip}^1$ requires an
eligible succedent in the first premise, while $\texttt{Snip}^2$ requires
an eligible antecedent in the second.

A natural first attempt is to represent eligibility as a predicate on
hypothesis variables directly, \texttt{LF elig\_h : lhypS A -> type},
adding eligibility witnesses to the context whenever a hypothesis is
introduced at an eligible position. This fails because LF contexts in
Beluga are structural: weakening is always available, so an
\texttt{elig\_h h} witness could be assumed for any variable without it
having been introduced by an axiom. The subformula property would then
break, since an arbitrarily weakened eligibility witness carries no
information about which axiom the variable came from, making it
impossible to extract a subformula relationship for the cut formula's
type.

Instead we define eligibility as predicates indexed directly over
derivation terms:

\begin{lstlisting}
LF elig_c : lconcS A -> type =
  | elig_c/l⊃L0S : {x : lhypS A} {y : lhypS (A ⊃ B)} elig_c (l⊃L0S x y)
and
LF elig_h : (lhypS A -> lconcS B) -> type =
  | elig_h/l⊃L0S   : {y : lhypS (A ⊃ B)} elig_h (\x. l⊃L0S x y)
  | elig_h/l⊗R0S/1 : {z : lhypS B}        elig_h (\y. l⊗R0S (y : lhypS A) z)
  | elig_h/l⊗R0S/2 : {y : lhypS A}        elig_h (\z. l⊗R0S y (z : lhypS B))
  | elig_h/l⊗R0S/3 :                       elig_h (\y. l⊗R0S y y)
\end{lstlisting}

\texttt{elig\_c~D} holds when the closed derivation \texttt{D} ends in
an axiom with an eligible succedent. \texttt{elig\_h~E} holds when the
function \texttt{E} maps its abstracted variable to an axiom in which
that variable occupies an eligible antecedent position. Because the
certificates are indexed over derivation terms rather than variables,
they cannot be introduced by weakening. This is what makes the
subformula property go through: the \texttt{elig} evidence identifies
the specific axiom the eligible formula came from, and from that a
subformula witness can be read off directly.

The four constructors of \texttt{elig\_h} enumerate every way a single
variable can appear eligibly in an axiom in our fragment. Three are
routine. The fourth, \texttt{elig\_h/l$\otimes$R0S/3}, covers the degenerate
case where both arguments of ${\otimes}R^0$ are the same variable, i.e.\
a derivation $\Gamma^0, x^* : A \vdash x : A \otimes A$. This arises
due to contraction in the intuitionistic setting and has no analogue in
a linear system. Extending the mechanization to additional connectives
requires only adding the corresponding \texttt{elig\_h} constructors for
each eligible position in the new axioms, along with the matching cases
in the proofs below.

This approach is related to the linearity predicates of Sano, Kavanagh,
and Pientka~\cite{Sanomech}, who encode linearity constraints for
session types as LF predicates within type judgments rather than using
linear contexts. Their predicates track a global resource-usage property
of channel variables; ours track a local positional property of a
specific occurrence within an axiom. A variable can be eligible in one
part of a derivation and ineligible in another, so the predicates are
indexed over derivation terms rather than variables to capture this
per-occurrence character.

\subsection{Translation Between $G_3$ and SAX}

Both directions of Theorem~1 are recursive functions over derivations
using a relation \texttt{rel-ctx-S} pairing the two contexts hypothesis
by hypothesis. Invertible rules are translated by applying the
corresponding constructor directly. The interesting cases are the
noninvertible rules, which appear as rules in $G_3$ but as zero-premise
axioms in SAX.

The direction from $G_3$ to SAX derives each noninvertible rule using
cuts and axioms. For instance, ${\supset}L$ is simulated by two nested
cuts against ${\supset}L^0$:

\begin{lstlisting}
rec seq2sax : (A : [|- o]) rel-ctx-S [Γ] [Γ'] -> [Γ |- conc A[]]
              -> [Γ' |- concS A[]] =
/ total 2 /
fn R D => case D of
  | [Γ |- ⊃L c1 (\h. c2) H] =>
    let [Γ' |- HS]                = hyp2hypS R [Γ |- H] in
    let [Γ' |- c1S]               = seq2sax R [Γ |- c1] in
    let [Γ', x : hypS B[] |- c2S] = seq2sax (cons-S R) [Γ, x : hyp _ |- c2] in
    [Γ' |- cutS (cutS c1S (\h. ⊃L0S h HS[..])) (\h. c2S)]  ...
\end{lstlisting}

The reverse direction derives each SAX axiom in $G_3$ using the
corresponding rule with identity proofs for the premises. For
${\supset}L^0$ this is one application of ${\supset}L$ with two identity
sub-derivations:

\begin{lstlisting}
rec sax2seq : (A : [|- o]) rel-S-ctx [Γ'] [Γ] -> [Γ' |- concS A[]]
              -> [Γ |- conc A[]] =
/ total 2 /
fn R D => case D of
  | [Γ' |- ⊃L0S HS1 HS2] =>
    let [Γ |- H1] = hypS2hyp R [Γ' |- HS1] in
    let [Γ |- H2] = hypS2hyp R [Γ' |- HS2] in
    [Γ |- ⊃L (initial H1) (\h. initial h) H2]  ...
\end{lstlisting}

\subsection{Admissibility of Cut and Cut Elimination}

Cut admissibility is proved as \texttt{cut-admis}, with totality
justified by induction on the cut formula. The cases fall into three
groups.

First, when the cut variable is in an eligible position in either
premise, the result is immediately a snip with no recursive call. For
example, when \begin{lstlisting}$D = \texttt{l⊃L0S~h1~h2}$ \end{lstlisting} the succedent is directly
eligible:

\begin{lstlisting}
  %% */_
  | ([Γ |- l⊃L0S h1 h2], [Γ, x : lhypS _ |- E]) =>
    [Γ |- lsnip1S (l⊃L0S h1 h2) (elig_c/l⊃L0S h1 h2) (\h. E[..,h])]
\end{lstlisting}

Second, when the cut formula is principal in both premises, the cut is
eliminated by substitution with a recursive call at a strictly smaller
type. The ${\supset}R / {\supset}L^0$ case requires a three-way split on
whether $h_1$ or $h_2$ in ${\supset}L^0$ is the cut variable $x$, since
$x$ may appear in an eligible position in $E$ even when $D$ is
${\supset}R$:

\begin{lstlisting}
  %% ⊃R/⊃L0
  | ([Γ |- l⊃RS (\h. D1)], [Γ, x : lhypS _ |- l⊃L0S h1 h2]) =>
    (case ([Γ, x : lhypS _ |- h2], [Γ, x : lhypS _ |- h1]) of
      | ([Γ, x:_ |- x],       [Γ, x:_ |- #h1[..]]) => [Γ |- D1[..,#h1]]
      | ([Γ, x:_ |- #h2[..]], [Γ, x:_ |- x])       =>
          [Γ |- lsnip2S (l⊃RS (\h. D1)) (\h. l⊃L0S h #h2[..])
                        (elig_h/l⊃L0S #h2[..])]
      | ([Γ, x:_ |- #h2[..]], [Γ, x:_ |- #h1[..]]) => [Γ |- l⊃L0S #h1 #h2]
    )
\end{lstlisting}

Third, when the cut formula is a side formula of the last rule, the cut
is commuted past that rule. When $E$ ends with a snip, the outer cut is
pushed inside both premises via two recursive calls; if eligibility is
lost the snip becomes a general cut, which is permitted since the
formula type is then a strict subformula of the cut type. A case worth
noting is $\texttt{\_/l} \otimes \texttt{R0S}$, which requires enumerating all combinations
of the cut variable $x$ appearing in the argument positions of the tensor
axiom, including the degenerate case where both positions are the same
variable:

\begin{lstlisting}
  | ([Γ |- D'], [Γ, x : lhypS _ |- l⊗R0S h1 h2]) =>
    (case ([Γ, x : lhypS _ |- h1], [Γ, x : lhypS _ |- h2]) of
      | ([Γ, x:_ |- #h1[..]], [Γ, x:_ |- #h2[..]]) => [Γ |- l⊗R0S #h1 #h2]
      | ([Γ, x:_ |- x],       [Γ, x:_ |- #h2[..]]) =>
          [Γ |- lsnip2S D' (\h. l⊗R0S h #h2[..])   (elig_h/l⊗R0S/1 #h2)]
      | ([Γ, x:_ |- #h1[..]], [Γ, x:_ |- x])        =>
          [Γ |- lsnip2S D' (\h. l⊗R0S #h1[..] h)   (elig_h/l⊗R0S/2 #h1)]
      | ([Γ, x : lhypS A[] |- x], [Γ, x : lhypS A[] |- x]) =>
          [Γ |- lsnip2S D' (\h. l⊗R0S h h) elig_h/l⊗R0S/3]
    )
\end{lstlisting}

Cut elimination over a separate \texttt{lconcS-cut} type then applies
\texttt{cut-admis} at each cut node after recursively processing the
sub-derivations:

\begin{lstlisting}
rec cut-elim : {Γ : lctxS} [Γ |- lconcS-cut A[]] -> [Γ |- lconcS A[]] =
/ total 1 /
mlam Γ => fn D => case D of
  | [Γ |- lcutS-cut D1 (\h. D2)] =>
    cut-admis _ _ (cut-elim _ [Γ |- D1]) (cut-elim _ [Γ, x : lhypS _ |- D2])
  | [Γ |- l⊃L0S-cut h1 h2]            => [Γ |- l⊃L0S h1 h2]
  | [Γ |- l⊗R0S-cut h1 h2]            => [Γ |- l⊗R0S h1 h2]
  | [Γ |- l⊗LS-cut (\h1. \h2. D1) h3] =>
    let [Γ, h1 : lhypS _, h2 : lhypS _ |- D1'] =
      cut-elim _ [Γ, h1 : lhypS _, h2 : lhypS _ |- D1] in
    [Γ |- l⊗LS (\h1. \h2. D1') h3]   ...
\end{lstlisting}

\subsection{Subformula Property}

We prove the subformula property in a more general form than the
statement in DeYoung et al.: the predicate \texttt{subfProp} is
parametrized over an arbitrary formula list $\Sigma$ rather than the
fixed set $\Gamma \cup \{A\}$. This generality is necessary because the
induction must extend $\Sigma$ when descending into premises that
introduce new hypotheses, and fixing $\Sigma$ at the top level would
require reconstructing the list at each step. The original statement is
recovered by instantiating $\Sigma = \Gamma \cup \{A\}$ at the root.

\begin{lstlisting}
inductive subfProp : {Γ : lctxS} {Σ : [|- formlist]}
                     {D : [Γ |- lconcS A[]]} ctype =
  | subfProp/initial :
      {#h : #[Γ |- lhypS A[]]} [|- inSig A Σ]
      -> subfProp [Γ] [|- Σ] [Γ |- linitialS #h]
  | subfProp/l⊃L0S :
      {#h1 : #[Γ |- lhypS A[]]} {#h2 : #[Γ |- lhypS (A[] ⊃ B[])]}
      [|- inSig A Σ] -> [|- inSig (A ⊃ B) Σ]
      -> subfProp [Γ] [|- Σ] [Γ |- l⊃L0S #h1 #h2]
  | subfProp/l⊗R0S :
      {#h1 : #[Γ |- lhypS A[]]} {#h2 : #[Γ |- lhypS B[]]}
      [|- inSig A Σ] -> [|- inSig B Σ]
      -> subfProp [Γ] [|- Σ] [Γ |- l⊗R0S #h1 #h2]
  | subfProp/lsnip1 :
      (D : [Γ |- lconcS A[]]) (E : [Γ, x : lhypS A[] |- lconcS B[]])
      {e : [Γ |- elig_c D]}
      subfProp [Γ] [|- Σ] [Γ |- D] -> [|- inSig A Σ]
      -> subfProp [Γ, x : lhypS A[]] [|- Σ] [Γ, x : lhypS A[] |- E]
      -> subfProp [Γ] [|- Σ] [Γ |- lsnip1S D e (\x. E[..,x])]
  | subfProp/lsnip2 :
      {e : [Γ |- elig_h (\x. E)]}
      subfProp [Γ] [|- Σ] [Γ |- D] -> [|- inSig A Σ]
      -> subfProp [Γ, x : lhypS A[]] [|- Σ] [Γ, x : lhypS A[] |- E]
      -> subfProp [Γ] [|- Σ] [Γ |- lsnip2S D (\x. E[..,x]) e]
  ...
\end{lstlisting}

Three helper lemmas support the main proof. \texttt{lookup} extracts a
membership proof from the context invariant \texttt{ctxInSig~$[\Gamma]$~[{$\vdash$}~{$\Sigma$}]},
which asserts that every formula type in $\Gamma$ is a subformula of
some element of $\Sigma$; given a hypothesis variable in $\Gamma$ it
returns an \texttt{inSig} proof for its type. \texttt{subf-trans}
establishes transitivity of the subformula relation by induction on its
second argument. \texttt{subf-inSig} promotes a subformula witness into
a list membership proof, used wherever the proof descends into a
sub-connective: given $B \leq A$ and $A \in \Sigma$ it produces
$B \in \Sigma$.

The main proof \texttt{subformula-property} proceeds by induction over
the structure of the derivation. In the snip cases the \texttt{elig}
evidence identifies the specific axiom the eligible formula came from,
and \texttt{subf-inSig} is called with the appropriate subformula
witness to produce \texttt{inSig A $\Sigma$}. The context invariant is then
extended via \texttt{ctxInSig/cons} and both premises proceed
recursively. The case for \texttt{elig\_h/l$\otimes$R0S/1~\#z}, for example,
extracts from the \texttt{inSig} proof for $A \otimes B$ a membership
proof for $A$:

\begin{lstlisting}
  | [Γ |- lsnip2S D' (\h. E') e] =>
    (case [Γ |- e] of
      ...
      | [Γ |- elig_h/l⊗R0S/1 #z] =>
        let ih_z   = lookup ci [Γ |- #z] in
        let isig_A = subf-inSig [|- subf/⊗1 subf/refl] goal in
        let ci'    = ctxInSig/cons ci isig_A in
        let sp_D   = subformula-property _ [Γ |- D'] ci isig_A in
        let sp_E   = subformula-property _ [Γ, h : lhypS _ |- E'] ci' goal in
        subfProp/lsnip2 _ sp_D isig_A sp_E
      ...
    )
\end{lstlisting}

This is precisely the point where the original predicate-on-variables
approach would fail: a weakened \texttt{elig\_h h} witness carries no
information about which axiom \texttt{h} came from, so there would be no
basis for the \texttt{subf-inSig} call. By indexing over derivation terms
instead, the \texttt{elig\_h/l$\otimes$R0S/1} constructor directly witnesses
that the abstracted variable is the first component of a tensor axiom,
from which the subformula relationship $A \leq A \otimes B$ is immediate.
Extending the mechanization to additional connectives requires adding the
corresponding \texttt{elig\_h} constructors, the matching cases in
\texttt{cut-admis}, and the appropriate \texttt{subf-inSig} calls in
\texttt{subformula-property}; the structure of each proof obligation is
uniform with what is presented here.

%\section{Contributions}
%\label{section:contribution}

%\subsection{Core Proof-Theoretic Results}

%Listed below are the proof-theoretic results that we have mechanized for our
%representative subset of SAX, covering identity ($\texttt{id}$), implication
%(${\supset}R$, ${\supset}L^0$), tensor (${\otimes}R^0$, ${\otimes}L$),
%and snips ($\texttt{snip}^1$, $\texttt{snip}^2$). 

%\begin{theorem}[Translations between $G_3$ and SAX]
  %$\Gamma \vdash A$ in $G_3$ iff $\Gamma \vdash A$ in SAX.
%\end{theorem}

%In the following theorems, we say a derivation is cut-free if it contains
%no uses of cut, but may contain snips.

%\begin{theorem}[Admissibility of Cut]
  %If there are cut-free derivations of $\Gamma \vdash x : A$ and
  %$\Gamma, x : A \vdash z : C$, then there exists a cut-free derivation
  %of $\Gamma \vdash z : C$.
%\end{theorem}

%\begin{theorem}[Cut Elimination in SAX]
  %If there is a derivation of $\Gamma \vdash x : A$, then there is a
  %cut-free derivation of the same sequent.
%\end{theorem}

%\begin{theorem}[Subformula Property]
  %All formulas in a cut-free derivation of $\Gamma \vdash x : A$ are
  %subformulas of formulas in $\Gamma$ or $A$.
%\end{theorem}


%\subsection{Encoding SAX in Beluga}

%% TODO add relevant code snippets


%\subsection{Eligibility and Irrelevance}

%\begin{lstlisting}
  %LF lconcS : o → type =
    %...
    %| l⊃RS : (lhypS A → lconcS B) → lconcS (A ⊃ B)
    %| l⊃L0S : lhypS A → lhypS (A ⊃ B) → lconcS B
    %...    
  %and
  %LF elig_c : lconcS A → type =
    %| elig_c/l⊃L0S : {x : lhypS A} {y : lhypS (A ⊃ B)}
                     %elig_c (l⊃L0S x y)
  %and
  %LF elig_h : (lhypS A → lconcS B) → type =
    %| elig_h/l⊃L0S : {y : lhypS (A ⊃ B)}
                     %elig_h (\x. l⊃L0S x y)
  %;
%\end{lstlisting}


%\subsection{Translation Between G3 and SAX}

%Theorem~1 states that $G_3$ and SAX derive the same sequents. We mechanize both
%directions as recursive functions over derivations that translate hypotheses
%between the two systems using a relation pairing up the two contexts hypothesis
%by hypothesis. Because SAX inherits the invertible rules from $G_3$, they are
%translated in both directions by directly applying the corresponding rule. The
%interesting cases are the noninvertible rules, which correspond to axioms in
%SAX.

%The direction from $G_3$ to SAX, showing that $G_3$ derives no more than SAX,
%proceeds by showing that each noninvertible $G_3$ rules can be derived using
%cuts and axioms. For instance, ${\supset}L$ which has no direct counterpart in
%SAX, can be simulated using two nested cuts against the axiom ${\supset}L^0$:
%\begin{lstlisting}
  %rec seq2sax : (A : [⊢ o]) rel-ctx-S [Γ] [Γ'] → [Γ ⊢ conc A[]] → [Γ' ⊢ concS A[]] =
  %/ total 2 /
  %fn R D ⇒ case D of
    %| [Γ ⊢ ⊃L c1 (\h. c2) H] ⇒
      %let [Γ' ⊢ HS] = hyp2hypS R [Γ ⊢ H] in
      %let [Γ' ⊢ c1S] = seq2sax R [Γ ⊢ c1] in
      %let [Γ', x : hypS B[] ⊢ c2S] = seq2sax (cons-S R) [Γ, x : hyp _ ⊢ c2] in
      %[Γ' ⊢ cutS (cutS c1S (\h. ⊃L0S h HS[..])) (\h. c2S)]
    %...
  %;
%\end{lstlisting}

%The other direction, from SAX to $G_3$, shows that each SAX axiom can be derived
%in $G_3$ using the corresponding rule and identity. For instance, $\supset L^0$
%is translated as an application of $\supset L$ in $G_3$ with identity proofs for
%both premises:
%\begin{lstlisting}
  %rec sax2seq : (A : [⊢ o]) rel-S-ctx [Γ'] [Γ] → [Γ' ⊢ concS A[]] → [Γ ⊢ conc A[]] =
  %/ total 2 /
  %fn R D ⇒ case D of
    %| [Γ' ⊢ ⊃L0S HS1 HS2] ⇒
      %let [Γ ⊢ H1] = hypS2hyp R [Γ' ⊢ HS1] in
      %let [Γ ⊢ H2] = hypS2hyp R [Γ' ⊢ HS2] in
      %[Γ ⊢ ⊃L (initial H1) (\h. initial h) H2]
    %...
  %;
%\end{lstlisting}


%\subsection{Admissibility of Cut and Cut Elimination}

%% Some representative cases, we can remove some or split them up but I'm not
%% sure which one we should actually keep
%\begin{lstlisting}
  %rec cut-admis : {Γ : lctxS} {A : [⊢ o]} [Γ ⊢ lconcS A[]]
                  %→ [Γ, x:lhypS A[] ⊢ lconcS C[]]
                  %→ [Γ ⊢ lconcS C[]] =
  %/ total 1 /
  %mlam Γ A ⇒ fn D E ⇒
  %case (D, E) of
    %%% */_ 
    %| ([Γ ⊢ l⊃L0S h1 h2], [Γ, x : lhypS _ ⊢ E]) ⇒
      %[Γ ⊢ lsnip1S (l⊃L0S h1 h2) (elig_c/l⊃L0S h1 h2) (\h. E[..,h])]
    %%% ⊃R/⊃L0
    %| ([Γ ⊢ l⊃RS (\h. D1)], [Γ, x : lhypS _ ⊢ l⊃L0S h1 h2]) ⇒
      %(case ([Γ, x : lhypS _ ⊢ h2], [Γ, x : lhypS _ ⊢ h1]) of
        %| ([Γ, x : lhypS _ ⊢ x], [Γ, x : lhypS _ ⊢ #h1[..] ]) ⇒
          %[Γ ⊢ D1[..,#h1]]
        %| ([Γ, x : lhypS _ ⊢ #h2[..]], [Γ, x : lhypS _ ⊢ x]) ⇒
          %[Γ ⊢ lsnip2S (l⊃RS (\h. D1)) (\h. l⊃L0S h #h2[..]) (elig_h/l⊃L0S #h2[..])]
        %| ([Γ, x : lhypS _ ⊢ #h2[..]], [Γ, x : lhypS _ ⊢ #h1[..]]) ⇒
          %[Γ ⊢ l⊃L0S #h1 #h2]
      %)
    %%% _/Snip1
    %| ([Γ ⊢ D], [Γ, x : lhypS _ ⊢ lsnip1S E1 e (\h. E2)]) ⇒
      %let [Γ ⊢ F1] = cut-admis _ _ [Γ ⊢ D] [Γ, x : lhypS _  ⊢ E1] in
      %let [Γ, x : lhypS _ ⊢ F2] =
        %cut-admis _ _ [Γ, y:lhypS _ ⊢ D[..]] [Γ, x : lhypS _, y : lhypS _ ⊢ E2[..,x]] in
      %cut-admis _ _ [Γ ⊢ F1] [Γ, y : lhypS _ ⊢ F2]
    %%% _/Snip2
    %| ([Γ ⊢ D], [Γ, x : lhypS _ ⊢ lsnip2S E1 (\h. E2) e]) ⇒
      %let [Γ ⊢ F1] = cut-admis _ _ [Γ ⊢ D] [Γ, x : lhypS _  ⊢ E1] in
      %let [Γ,  x : lhypS _ ⊢ F2] =
        %cut-admis _ _ [Γ, y:lhypS _ ⊢ D[..]] [Γ, x : lhypS _, y : lhypS _ ⊢ E2[..,x]] in
      %cut-admis _ _ [Γ ⊢ F1] [Γ, y : lhypS _ ⊢ F2]
    %...
    %;
%\end{lstlisting}

%% `cut-elim` is less interesting, the type signature is enough
%\begin{lstlisting}
  %rec cut-elim : {Γ : lctxS} [Γ ⊢ lconcS-cut A[]] → [Γ ⊢ lconcS A[]] = ...
%\end{lstlisting}


%\subsection{Subformula Property}

%\begin{lstlisting}
  %inductive subfProp : {Γ : lctxS} {Σ : [⊢ formlist]} {D : [Γ ⊢ lconcS A[]]} ctype =
    %| subfProp/lsnip1 :
        %(D : [Γ ⊢ lconcS A[]])
        %(E: [Γ, x : lhypS A[] ⊢ lconcS B[]])
        %{e : [Γ ⊢ elig_c D]}
        %subfProp [Γ] [⊢ Σ] [Γ ⊢ D]
        %→ [⊢ inSig A Σ]
        %→ subfProp [Γ, x : lhypS A[]] [⊢ Σ] [Γ, x : lhypS A[] ⊢ E]
        %→ subfProp [Γ] [⊢ Σ] [Γ ⊢ lsnip1S D e (\x. E[.., x])]
    %| subfProp/lsnip2 :
        %{e : [Γ  ⊢ elig_h (\x. E)]}
        %subfProp [Γ] [⊢ Σ] [Γ ⊢ D]
        %→ [⊢ inSig A Σ]
        %→ subfProp [Γ, x : lhypS A[]] [⊢ Σ] [Γ, x : lhypS A[] ⊢ E]
        %→ subfProp [Γ] [⊢ Σ] [Γ ⊢ lsnip2S D (\x. E[.., x]) e]
    %...
    %;
%\end{lstlisting}


%\begin{lstlisting}
  %rec subformula-property : {Γ : lctxS} {D : [Γ ⊢ lconcS A[]]}
                            %→ ctxInSig  [Γ] [⊢ Σ]
                            %→ [⊢ inSig A Σ]
                            %→ subfProp [Γ] [⊢ Σ] [Γ ⊢ D] =
  %/ total 1 /
  %mlam Γ D ⇒ fn ci goal ⇒
  %case [Γ ⊢ D] of
    %| [Γ ⊢ lsnip1S D' e (\h. E')] ⇒
      %(case [Γ ⊢ e] of
        %| [Γ ⊢ elig_c/l⊃L0S #h1 #h2] ⇒
          %let ih2    = lookup ci [Γ ⊢ #h2] in
          %let isig_B = subf-inSig [⊢ subf/⊃2 subf/refl] ih2 in
          %let ih1    = lookup ci [Γ ⊢ #h1] in
          %let sp_D   = subfProp/l⊃L0S [Γ ⊢ #h1] [Γ ⊢ #h2] ih1 ih2 in
          %let ci'    = ctxInSig/cons ci isig_B in
          %let sp_E   = subformula-property _ [Γ, h : lhypS _ ⊢ E'] ci' goal in
          %subfProp/lsnip1 _ sp_D isig_B sp_E
      %)
    %| [Γ ⊢ lsnip2S D' (\h. E') e] ⇒
      %(case [Γ ⊢ e] of
        %| [Γ ⊢ elig_h/l⊃L0S #y] ⇒
          %let ih_y   = lookup ci [Γ ⊢ #y] in
          %let isig_A = subf-inSig [⊢ subf/⊃1 subf/refl] ih_y in
          %let ci'    = ctxInSig/cons ci isig_A in
          %let sp_D   = subformula-property _ [Γ ⊢ D'] ci isig_A in
          %let sp_E   = subformula-property _ [Γ, h : lhypS _ ⊢ E'] ci' goal in
          %subfProp/lsnip2 _ sp_D isig_A sp_E
      %)
    %...      
    %;

%\end{lstlisting}